Predicting sales of newly published books

### 2015-08-18 paper.tex
traduciendo los nombres de variables

\begin{minipage}{2.3in} \begin{verbatim}
referencia
autor
pvp
materia1
materia2
materia3
editorial
coleccion
encuadernacion
tirada
venta_total
venta_grandes_superficies
venta_delegados
venta_resto
venta1anio_total
venta1anio_grandes_superficies
venta1anio_delegados
venta1anio_resto
colocado_total
colocado_grandes_superficies
colocado_delegados
colocado_resto
colocado1anio_total
colocado1anio_grandes_superficies
colocado1anio_delegados
\end{verbatim} \end{minipage}     &

\begin{minipage}{2.3in} \begin{verbatim}
colocado1anio_resto
reimpresiones
numero_reimpresiones
devolucion_total
devolucion_grandes_superficies
devolucion_delegados
devolucion_resto
devolucion1anio_total
devolucion1anio_grandes_superficies
devolucion1anio_delegados
devolucion1anio_resto
obsequios
ejemplares_distribuidos_en_novedad
puntos_vta_total
puntos_vta_grandes_superficies
puntos_vta_delegados
puntos_vta_resto
puntos_vta1anio_total
puntos_vta1anio_grandes_superficies
puntos_vta1anio_delegados
puntos_vta1anio_resto
semanas_venta
entorno_venta_positivo
entorno_venta_medio
entorno_venta_negativo
\end{verbatim} \end{minipage}    \\

@@

\begin{minipage}{2.3in} \begin{verbatim}
puntos_vta1anio_grandes_superficies
venta1anio_resto
entorno_venta_negativo
colocado1anio_grandes_superficies
devolucion_total
reimpresiones
venta1anio_grandes_superficies
puntos_vta1anio_total
ejemplares_distribuidos_en_novedad
tirada
numero_reimpresiones
devolucion_grandes_superficies
puntos_vta1anio_resto
venta_resto
puntos_vta_delegados
devolucion_resto
puntos_vta1anio_delegados
entorno_venta_positivo
colocado1anio_resto
puntos_vta_resto
devolucion1anio_total
devolucion_delegados
\end{verbatim} \end{minipage}     &

\begin{minipage}{2.3in} \begin{verbatim}
venta_grandes_superficies
colocado1anio_total
puntos_vta_total
colocado_grandes_superficies
colocado1anio_delegados
puntos_vta_grandes_superficies
venta1anio_total
entorno_venta_medio
semanas_venta
colocado_delegados
autor
venta1anio_delegados
obsequios
devolucion1anio_grandes_superficies
venta_delegados
colocado_resto
devolucion1anio_delegados
colocado_total
devolucion1anio_resto
pvp
venta_total (output)
\end{verbatim} \end{minipage}    \\

>>>>

\begin{minipage}{2.3in} \begin{verbatim}
REFERENCE
AUTHOR
RETAIL PRICE
SUBJECT-MATTER1
SUBJECT-MATTER2
SUBJECT-MATTER3
EDITORIAL
COLLECTION
BOOKBINDING
PRINT-RUN
TOTAL SALES
MALLS SALES
DELEGATES SALES
REST OF SALES
TOTAL SALES FIRST YEAR
MALL SALES FIRST YEAR
DELEGATES SALES FIRST YEAR
REST OF SALES FIRST YEAR
TOTAL DISTRIBUTED
MALLS DISTRIBUTED
DELEGATES DISTRIBUTED
REST OF DISTRIBUTED
TOTAL DISTRIBUTED FIRST YEAR
MALLS DISTRIBUTED FIRST YEAR
DELEGATES DISTRIBUTED FIRST YEAR
\end{verbatim} \end{minipage}     &

\begin{minipage}{2.3in} \begin{verbatim}
REST OF DISTRIBUTED FIRST YEAR
REPRINTS
NUMBER OF REPRINTS
TOTAL DEVOLUTIONS
MALLS DEVOLUTIONS
DELEGATES DEVOLUTIONS
REST OF DEVOLUTIONS
TOTAL DEVOLUTIONS FIRT YEAR
MALLS DEVOLUTIONS FIRST YEAR
DELEGATES DEVOLUTIONS FIRST YEAR
REST OF DEVOLUTIONS FIRST YEAR
GIFTS
UNITS DISTRIBUTED IN FIRST EDITION
TOTAL SELLING POINTS
MALLS SELLING POINTS
DELEGATES SELLING POINTS
REST OF SELLING POINTS
TOTAL SELLING POINTS FIRST YEAR
MALLS SELLING POINTS FIRST YEAR
DELEGATES SELLING POINTS FIRST YEAR
REST OF SELLING POINTS FIRST YEAR
WEEKS ON SALE
POSITIVE SALE MARKET
MEDIUM SALE MARKET
NEGATIVE SALE MARKET
\end{verbatim} \end{minipage}    \\

@@

\begin{minipage}{2.3in} \begin{verbatim}
MALLS SELLING POINTS FIRST YEAR
REST OF SALES FIRST YEAR
NEGATIVE SALE MARKET
MALLS DISTRIBUTED FIRST YEAR
TOTAL DEVOLUTIONS
REPRINTS
MALL SALES FIRST YEAR
TOTAL SELLING POINTS FIRST YEAR
UNITS DISTRIBUTED IN FIRST EDITION
PRINT-RUN
NUMBER OF REPRINTS
MALLS DEVOLUTIONS
REST OF SELLING POINTS FIRST YEAR
REST OF SALES
DELEGATES SELLING POINTS
REST OF DEVOLUTIONS
DELEGATES SELLING POINTS FIRST YEAR
POSITIVE SALE MARKET
REST OF DISTRIBUTED FIRST YEAR
REST OF SELLING POINTS
TOTAL DEVOLUTIONS FIRT YEAR
DELEGATES DEVOLUTIONS
\end{verbatim} \end{minipage}     &

\begin{minipage}{2.3in} \begin{verbatim}
MALLS SALES
TOTAL DISTRIBUTED FIRST YEAR
TOTAL SELLING POINTS
MALLS DISTRIBUTED
DELEGATES DISTRIBUTED FIRST YEAR
MALLS SELLING POINTS
TOTAL SALES FIRST YEAR
MEDIUM SALE MARKET
WEEKS ON SALE
DELEGATES DISTRIBUTED
AUTHOR
DELEGATES SALES FIRST YEAR
GIFTS
MALLS DEVOLUTIONS FIRST YEAR
DELEGATES SALES
REST OF DISTRIBUTED
DELEGATES DEVOLUTIONS FIRST YEAR
TOTAL DISTRIBUTED
REST OF DEVOLUTIONS FIRST YEAR
RETAIL PRICE
TOTAL SALES (output)
\end{verbatim} \end{minipage}    \\
